\documentclass{article}

\pagestyle{headings}

\title{SUMMARY}
\author{WANG Chen, 2015213086, wangchen@bupt.edu.cn}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\newpage
\section{INTRODUCTION}

This is a summary for development of simple shell program named msh.
The shell program is a course assignment in \emph{Advanced Programming in the UNIX Environment}.
It will make us have a deeper understanding in UNIX C programming, after we finish this program.
This summary is contains related information about this program, the process of development, work plan and comments.

\section{WORK PLAN}

\begin{table}[h]
\centering
\begin{tabular}{|l|c|}
\hline
 & Time(nums of week) \\ \hline
Requirement Analysis & 1 \\ \hline
Detail Design & 2 \\ \hline
Coding & 3 \\ \hline
Test & 2 \\ \hline
Document Filing & 1 \\ \hline
\end{tabular}
\caption{Work Plan}
\label{workPlan}
\end{table}

Table \ref{workPlan} show the work plan of development of the shell program.

We use 1 week to analyze the requirement of project, and write the requirement analysis document.

Detail design was taken 2 weeks to be finished, and it include the information about functions we need to implement for meeting requirements.

Based on detail design document, we take 3 weeks to write the code of program. Some part of detail design were modified when we wrote the code for solving problems.

2 weeks were taken for testing.,We test the program to verify that the program meet all requirement in requirement analysis document.

Finally, we took 1 week for document filing, and finished this project.

\section{COMMENTS}

In this project, we designed and built a simple shell program according to the requirements of assignment.
It is a shell that can realize some simple functions like \verb|cd|, \verb|exit|, \verb|ls| and so on.
We use the knowledge about input and output redirection, I/O of file, command execution and environment variable to code this shell program. And an entire software development process was taken to finish this program. The result include  shell program, requirement analysis, detail design, test report, summary, user manual and readme documents.
In this process, we got a better understanding on not only how a shell program is running in UNIX environment, but also the process of software development.

\newpage
\section{RELATED INFORMATION}

Following documents can be found in the same folder.

\begin{enumerate}
\item Requirement analysis
\item Detail design
\item User manual
\item Test report
\item README
\end{enumerate}

\section{DEVELOPMENT ENVIRONMENT}

\begin{itemize}
\item Hardware: Macbook pro 2018
\item System: Mac OS 10.14.4
\item Code Software: Visual Studio Code
\item Compiler: GCC 4.2.1
\end{itemize}

\end{document}